### 2018-11-15 manuscript/manuscript.rmd
Re-organized the repo as per #7 . Links to files are probably broken and need to be fixed

### Alignment composition

@@

a_file = "~/Desktop/animal_root/blast/phylips/Chang2015_Chang2015.phy"
p_file = "~/Desktop/animal_root/blast/phylips/Chang2015_Chang2015.nex"
msa = PartitionedMultipleAlignment( a_file, p_file, taxa )

@@

**Fig XXTaxon_composition.** Each of the primary matrices considered here, color coded by the types of genes sampled (XX Ribosomal proteins, etc). Horizontal size is proportional to the number of genes sampled, vertical size to the number of taxa sampled.

### Alignment overlap

>>>>

### Matrix taxon composition

@@

phylip_file_names = list.files(pattern = "blast/phylips/.+\\.phy$")

a_file = "blast/phylips/Chang2015_Chang2015.phy"
p_file = "blast/phylips/Chang2015_Chang2015.nex"
msa = PartitionedMultipleAlignment( a_file, p_file, taxa )

@@

### Matrix gene composition

```{r gene_composition}

partition_clusters = 
	read_tsv( "blast/graphs/diamond_partition_clusters.tsv" ) %>% 
	dplyr::rename( partition=partition_name ) %>%
	dplyr::rename( matrix=dataset ) %>%
	dplyr::rename( cluster_id=cluster_number )

busco_results = 
	read_tsv("blast/graphs/busco_metazoa_results.tsv") %>% 
	filter( Status != "Missing" )

sequences_all_txt = 
	read_tsv("blast/all_parts_list.txt")

names(sequences_all_txt) = c("full_name")
sequences_all = str_split_fixed( sequences_all_txt$full_name, ":", 5 ) %>% 
	as_tibble()
names( sequences_all ) = c( "manuscript", "matrix", "species", "ncbi_taxon_id", "partition" )

partitions_all = 
	sequences_all %>% 
	group_by( manuscript, matrix, partition ) %>% 
	summarise( n_sequences =n() )

# Multiple fields are in one colon delimited string. Need to parse them out.
# Busco result example
# "Moroz2014:ED3a:Capitella:51293:0241"  
# manuscript:matrix:species:NCBI_taxon_id:partition

Bs = 
	str_split_fixed( busco_results$Sequence, ":", 5 ) %>% 
	as_tibble()

names( Bs ) = c( "manuscript", "matrix", "species", "ncbi_taxon_id", "partition" )

Bs %<>% mutate( ncbi_taxon_id = as.integer(ncbi_taxon_id) )

busco_results %<>% bind_cols( Bs )

# Find overrepresented partitions, ie partitions with genes that hit more than one Busco
busco_distinct =  busco_results %>% select( manuscript, matrix, partition, Description ) %>% distinct(  )
busco_overrepresented = busco_distinct %>% group_by( manuscript, matrix, partition ) %>% summarise( n = n() ) %>% filter( n > 1 )
busco_overrepresented
busco_overrepresented_full = left_join( busco_overrepresented, busco_results )

# Combine and summarize results
partition_to_busco_map = 
	busco_distinct %>% 
	group_by( manuscript, matrix, partition ) %>% 
	summarise( BUSCO=names(which(table(Description) == max(table(Description)))[1]) )

partition_clusters %<>% left_join( partition_to_busco_map, by=c("manuscript", "matrix", "partition") )

busco_summary = 
	partition_to_busco_map %>% 
	group_by( manuscript, matrix ) %>%
	summarise( n_busco_partitions = n() )

matrix_summary =
	partitions_all %>%
	group_by( manuscript, matrix ) %>%
	summarise( n_partitions = n() ) %>%
	left_join(
		busco_summary,
		by=c("manuscript", "matrix")
	)

ggplot( matrix_summary ) +
	geom_point( aes(x=n_partitions, y=n_busco_partitions, col=manuscript) ) + geom_abline(slope=1,intercept=0) + coord_fixed()

cluster_summary =
	partition_clusters %>% 
	group_by( cluster_id ) %>% 
	summarise( 
		n_partitions = n(), 
		n_matrices= length(unique(matrix)),
		n_with_busco = sum(! is.na(BUSCO)),
		n_unique_busco = length(unique(na.omit(BUSCO)))
	)

**Fig XXBUSCO_annotations.** The number of partitions with BUSCO annotations in each matrix, relative to the number of partitions.

**Fig XXGene_composition.** Each of the primary matrices considered here, color coded by the types of genes sampled (XX Ribosomal proteins, etc). Horizontal size is proportional to the number of genes sampled, vertical size to the number of taxa sampled.

### Matrix overlap
